AD Target Gene Report

### 2020-01-20 code/02-Master.Rmd
Gene Name Munger

```{r yamlIMPT, eval = T, include=T}
#Assign your YAML formated config file to a varable
configuration <- "YAML_FILE"
config <- read_yaml(configuration)

@@

#DE  = 'syn14237651'
#eQTL_Cer = 'syn16984411'
#eQTL_TCX = 'syn16984410'
#eQTL_DLPFC = 'syn16984409'
#eQTL_EasyYesNo = 'syn12514912
#AgoraDrugability = 'syn13363443'
#Proteomics = 'syn18689335'
#AD Associated Mets Networks: syn11932957
#AD Meta Network Modual Associations syn11954640
```
```{r Module1, eval = T, include=T}

@@

>>>>

```{r yamlIMPT, eval = T, include=T}
#Assign your YAML formated config file to a varable
configuration <- "YAML_FILE"
config <- read_yaml(file=paste0('./',configuration))

@@

#DE  = 'syn14237651'
#eQTL_Cer = 'syn16984411'
#eQTL_TCX = 'syn16984410'
#eQTL_DLPFC = 'syn16984409'
#eQTL_EasyYesNo = 'syn12514912
#AgoraDrugability = 'syn13363443'
#Proteomics = 'syn18689335'
#AD Associated Mets Networks: syn11932957
#AD Meta Network Modual Associations syn11954640
```

Importing genelist `r thisFile` as `r config$genelisttype`
```{r GeneNames, eval=T, include=T}

GeneData <- function( id, type ){
  #Retreives gene name info
  #'@id the gene ids to source a list from
  #'@type either ENSG or GNAME for type of gen ids

  org = 'hsa'
  host = 'grch37.ensembl.org'
  ensembl <- useMart("ENSEMBL_MART_ENSEMBL", host = host)
  ds <- listDatasets(ensembl)[, "dataset"]
  ds <- grep(paste0("^", org), ds, value = TRUE)

  if (length(ds) == 0){
    stop(paste("Mart not found for:", org))
  } else if (length(ds) > 1) {
    message("Found several marts")
    sapply(ds, function(d) message(paste(which(ds == d), d, sep = ": ")))
    n <- readline(paste0("Choose mart (1-", length(ds), ") : "))
    ds <- ds[as.integer(n)]
  }

  if(type == 'ENSG'){
    id.type = 'ensembl_gene_id'
    ensembl <- useDataset(ds, mart = ensembl)
    Genes <- getBM(filters = id.type, attributes = c(id.type, 'hgnc_symbol', 'chromosome_name', 'start_position', 'end_position'), values = id, mart = ensembl)
  }else{
    if(type == 'GNAME'){
      id.type = 'hgnc_symbol'
      ensembl <- useDataset(ds, mart = ensembl)
      Genes <- getBM(filters = id.type, attributes = c('ensembl_gene_id', id.type, 'chromosome_name', 'start_position', 'end_position'), values = id, mart = ensembl)
      ##Cut Decmals
    }else{
      #Error Gene names not specififed correctly
      stop("ERROR: SOURCE=Config.yaml Issue=genelisttype must be ENSG or GNAME")
    }
  }
  return(Genes)
}

#Load Gene Set:
Genes <- read.table( paste0(config$filedir, '/genelists/', config$genelistfile ), header=F, sep='\t')

Tab <- GeneData( Genes, config$genelisttype )
Tab$Coord_hg19 <- paste0("chr", Tab$chromosome_name, ":", Tab$start_position, "-",Tab$end_position)
Tab$Interval_hg19 <- NA
for( i in 1:dim(Tab)[1]){
  if(  Tab$start_position[i] < Tab$ensembl_gene_id[i] ){
    Tab$Interval_hg19[i] <- paste0("chr", Tab$chromosome_name[i], ":", as.numeric(Tab$start_position[i])-1e6, "-", as.numeric(Tab$end_position[i])+1e6)
  }else{
    Tab$Interval_hg19[i] <- paste0("chr", Tab$chromosome_name[i], ":", as.numeric(Tab$start_position[i])+1e6, "-", as.numeric(Tab$end_position[i])-1e6)
  }
}

@@

```{r Module1, eval = T, include=T}
if( i %in% config$modules ){
  writeLines('Modeling and ranking genelist ', config$genelistfile ,' by IGAP SNP evidence')

  source()

}else{
  writeLines('Skipping IGAP based Model and Gene-Ranking: User specified module 1 not included in <Config>.yaml ')
}

### 2020-01-20 code/03-Run.Rmd
Arange preamble
Gene Name Munger

```{r yamlIMPT, eval = F, include=FALSE}
#Assign your YAML formated config file to a varable
YAML_Config <- "YAML_FILE"

setwd("~/AD_TargetRank/")
source("~/AD_TargetRank/utilityFunctions/knitfile2synapseClient.R")
source("~/AD_TargetRank/utilityFunctions/hook_synapseMdSyntax_plot.R")
createAndKnitToFolderEntityClient(file = "CMC_ACC_Exp_DataProcessing_V2.Rmd",
                                          parentId ="syn21478397",
                                          folderName = 'ACC')

#Test Genes
Genes <- c('ENSG00000081189','ENSG00000086288', 'ENSG00000137845', 'ENSG00000138600', 'ENSG00000173157', 
           'ENSG00000134463', 'ENSG00000156170', 'ENSG00000120899', 'ENSG00000147065','ENSG00000130203', 
           'ENSG00000165025','ENSG00000174628', 'ENSG00000265148', 'ENSG00000159640', 'ENSG00000154734', 
           'ENSG00000136717', 'ENSG00000095970', 'ENSG00000120885', 'ENSG00000064687')

#Ana's genes
Genes <- c("ENSG00000048392", "ENSG00000051620", "ENSG00000070495", "ENSG00000074800", "ENSG00000077152", "ENSG00000091140", "ENSG00000096060", "ENSG00000100030", "ENSG00000100418", "ENSG00000100605", "ENSG00000105220", "ENSG00000105398", "ENSG00000108424", "ENSG00000109576", "ENSG00000111640", "ENSG00000113657", "ENSG00000117115", "ENSG00000117228", "ENSG00000119125", "ENSG00000121879", "ENSG00000128683", "ENSG00000130540", "ENSG00000136634", "ENSG00000137992", "ENSG00000139112", "ENSG00000140374", "ENSG00000143546", "ENSG00000146701", "ENSG00000146733", "ENSG00000155368", "ENSG00000156709", "ENSG00000162433", "ENSG00000164111", "ENSG00000165025", "ENSG00000166224", "ENSG00000167325", "ENSG00000167720", "ENSG00000168291", "ENSG00000176490", "ENSG00000177511", "ENSG00000186298", "ENSG00000196154", "ENSG00000197448", "ENSG00000197956", "ENSG00000213719")

#Genes <- c('ENSG00000147065','ENSG00000130203')
#Genes <- c('ENSG00000130203')
Tissues <- c('CBE',  'DLPFC' , 'FP', 'IFG', 'PHG', 'STG', 'TCX')
#DE  = 'syn14237651'
#eQTL_Cer = 'syn16984411'
#eQTL_TCX = 'syn16984410'
#eQTL_DLPFC = 'syn16984409'
#eQTL_EasyYesNo = 'syn12514912
#AgoraDrugability = 'syn13363443'
#Proteomics = 'syn18689335'
#AD Associated Mets Networks: syn11932957
#AD Meta Network Modual Associations syn11954640
```

```{r Settings, echo =F, warning=F}
plotdir='/Users/jgockley/Desktop/Projects/AMP-AD_Targets/Candidate_Target_Profiler/Plots/'
tabledir='Tables/'
Tissues <- c('CBE', 'DLPFC', 'IFG', 'PHG', 'TCX', 'STG', 'FP')

@@

>>>>

```{r yamlIMPT, eval = T, include=T}
#Assign your YAML formated config file to a varable
configuration <- "configs/TestConfig.yaml"
config <- read_yaml(configuration)

setwd(config$filedir)
plotdir=paste0( 'runs/', config$runname, '/figures' )
tabledir=paste0( 'runs/', config$runname, '/tables' )

Tissues <- config$tissue

#DE  = 'syn14237651'
#eQTL_Cer = 'syn16984411'
#eQTL_TCX = 'syn16984410'
#eQTL_DLPFC = 'syn16984409'
#eQTL_EasyYesNo = 'syn12514912
#AgoraDrugability = 'syn13363443'
#Proteomics = 'syn18689335'
#AD Associated Mets Networks: syn11932957
#AD Meta Network Modual Associations syn11954640
```

```{r Process, eval=T, include=T}

  writeLines('Importing genelist ', config$genelistfile, ' as ', config$Genelisttype)

@@

```{r GeneNames, eval=T, include=T}
GeneData <- function( id ){

  org = 'hsa'
  id.type = 'ensembl_gene_id'
  #host = 'jul2019.archive.ensembl.org'
  host = 'grch37.ensembl.org'
  ensembl <- useMart("ENSEMBL_MART_ENSEMBL", host = host)
  ds <- listDatasets(ensembl)[, "dataset"]
  ds <- grep(paste0("^", org), ds, value = TRUE)

  if (length(ds) == 0){
    stop(paste("Mart not found for:", org))
  } else if (length(ds) > 1) {
    message("Found several marts")
    sapply(ds, function(d) message(paste(which(ds == d), d, sep = ": ")))
    n <- readline(paste0("Choose mart (1-", length(ds), ") : "))
    ds <- ds[as.integer(n)]
  }

  ensembl <- useDataset(ds, mart = ensembl)

  Genes <- getBM(filters = id.type, attributes = c(id.type, 'hgnc_symbol', 'chromosome_name', 'start_position', 'end_position'), values = id, mart = ensembl)
  return(Genes)
}

Tab <- GeneData( Genes )
Tab$Coord_hg19 <- paste0("chr", Tab$chromosome_name, ":", Tab$start_position, "-",Tab$end_position)
Tab$Interval_hg19 <- NA
for( i in 1:dim(Tab)[1]){
  if(  Tab$start_position[i] < Tab$ensembl_gene_id[i] ){
    Tab$Interval_hg19[i] <- paste0("chr", Tab$chromosome_name[i], ":", as.numeric(Tab$start_position[i])-1e6, "-", as.numeric(Tab$end_position[i])+1e6)
  }else{
    Tab$Interval_hg19[i] <- paste0("chr", Tab$chromosome_name[i], ":", as.numeric(Tab$start_position[i])+1e6, "-", as.numeric(Tab$end_position[i])-1e6)
  }
}

```
```{r Module1, eval = T, include=T}
if( i %in% config$modules ){
  writeLines('Modeling and ranking genelist ', config$genelistfile ,' by IGAP SNP evidence')

  source()

}else{
  writeLines('Skipping IGAP based Model and Gene-Ranking: User specified module 1 not included in <Config>.yaml ')
}
